Monitoring and predictive mapping of floristic biodiversity along a climatic gradient in ENSO's terrestrial core region, NW Peru

### 2020-08-11 text/ecography/round_3/enso_comp.Rmd
replace source() by load_all()

```{r varpart, echo=FALSE, out.width="70%", fig.align="center", message=FALSE, fig.cap="Fractions explaining the floristic composition represented by the first two DCA axes in accordance with a RDA variation partitioning. Numbers within the circles represent the adjusted $R^2$. Significance levels of the pure fractions are given in the soil and topography circles as . ($<0.1$), * ($<0.05$), ** ($ <0.01$), and *** ($<0.001$)."}
# include_graphics(here("figures/16_varpart.png"))
# Variation partitioning for the four londo cts
# attach packages
library("vegan")
library("dplyr")
# read in functions
source(here("code/funs/varpart_helper_funs.R"))

>>>>

```{r varpart, echo=FALSE, out.width="70%", fig.align="center", message=FALSE, fig.cap="Fractions explaining the floristic composition represented by the first two DCA axes in accordance with a RDA variation partitioning. Numbers within the circles represent the adjusted $R^2$. Significance levels of the pure fractions are given in the soil and topography circles as . ($<0.1$), * ($<0.05$), ** ($ <0.01$), and *** ($<0.001$)."}
# include_graphics(here("figures/16_varpart.png"))
# Variation partitioning for the four londo cts
# attach packages
library("vegan")
library("dplyr")
# attach own functions
devtools::load_all()
